Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
z

  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df0 # selected time span
  }

  df <- df %>% filter(catalog == catalogue)

@@

# Calculate percentages
dff <- spread(df, language, n, fill = 0)
dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
#dff <- gather(dff, publication_decade);
dff <- melt(dff, "publication_decade");
colnames(dff) <- c("publication_decade", "language", "f")
dff$language <- factor(dff$language, levels = langs)

theme_set(theme_bw(20))
p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
     xlab("Publication year") +
     ylab("Title count frequency (%)") +
     ggtitle(paste("Languages (", catalogue, ")", sep = ""))
print(p)

>>>>

  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df.full # full time span
  }

  df <- df %>% filter(catalog == catalogue)%>%
        filter(publication_year >= 1600 & publication_year <= 1900)

@@

# Calculate percentages
dff <- spread(df, language, n, fill = 0)
dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
#dff <- gather(dff, publication_decade);
dff <- melt(dff, "publication_decade");
colnames(dff) <- c("publication_decade", "language", "f")
#dff$language <- factor(dff$language, levels = langs)

theme_set(theme_bw(20))
p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
     xlab("Publication year") +
     ylab("Title count frequency (%)") +
     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +  scale_fill_brewer(palette="Paired")
print(p)
